Title

### 2023-05-16 main.tex
Pequeño arreglo 2

This theorem implies that starting from the state $|0\rangle$,
the only curves of states we could expect to create
with a 1PR circuit are those of the form
\begin{equation}
|\eta(p)\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is},
\label{eq:curve-states}
\end{equation}
with 
\begin{equation}
|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1  \; \text{and} \; \vec{a}, \vec{b}, \vec{c} \; \text{orthogonal vectors}.
\label{eq:conditions-vecs}
\end{equation}
Furthermore, we can exhibit a way to create any of these curves of states
with a 1PR circuit.
To do it, we can use the circuit of \fref{fig:1PR-circuit} with the parametrized
rotation $R$ on the last qubit controlled by all the other qubits
and matrices $A$ and $B$ defined as:
\begin{align*}
B = (\vec{d}, *,*, \cdots,*), \; 
A = (* , \cdots, *, \vec{c}/|\vec{c}|, \vec{b}/|\vec{b}|, \vec{a}/|\vec{a}|).
\end{align*}
Here the column vector $\vec{d}$ is defined as 
$(0,0, \cdots,0 ,|\vec{c}|, |\vec{b}|, |\vec{a}|)^T$
and the asterisks can be completed in any
way such that these matrices are unitary.
Then, starting from the initial state $|0\rangle = (1,0,0,\cdots,0)$
and applying the matrices $ARB$ defined
like this, some direct calculations lead us  to 
the resulting curve of states
of \eref{eq:curve-states}.

@@

We can now use the last theorem to conclude directly which Pauli dynamical maps
can be implemented using a 1PR circuit.
With this condition, the curve of states of \eref{eq: parametrized state} 
has to be created on the ancilla qubits with only one parametrized curve. 
Therefore, the results of the last section imply that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is},
\end{eqnarray}
where $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors in $\mathbb{C}^{2n}$ 
and $|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2= 1$.

For the particular case of one qubit,
we can show some examples of Pauli dynamical maps that can be
implemented with a 1PR circuit, which are plotted
in \fref{fig:curves}.

@@

\begin{itemize}
\item \textbf{Bit flip map:} 
This dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1
\end{align*}
for $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
$|\beta_0(p)|^2= (1-p)^2$, $|\beta_1(p)|^2 = p$, $|\beta_2(p)|^2 = |\beta_3(p)|^2 = 0$.
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = \left(\sqrt{1-p},\sqrt{p},0,0\right).
\end{align*}
This can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is} \left( \dfrac{1}{2}, - \dfrac{i}{2},0,0 \right) + e^{-is} \left( \dfrac{1}{2}, \dfrac{i}{2},0,0 \right),
\end{align*}
with $s= \arcsin(\sqrt{p})$.
Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
and it can be created with a 1PR circuit.
The exact same thing can be done
for the phase flip and bit phase flip dynamical maps
changing $\sigma_1$ with
$\sigma_3$ and $\sigma_2$ respectively.

@@

\item \textbf{Parabolic dynamical map:} Finally, we define the parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} (1-p)^2 \sigma_0 \rho \sigma_0 + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{eqnarray}
|\beta(p)\rangle = \left(\dfrac{1}{2} (1-p) , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2}(1+p) \right).
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle = \left( \dfrac{1}{2},0,0, \dfrac{1}{2} \right) + e^{is} \left( \dfrac{i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{-i}{4} \right) + e^{-is}  \left( \dfrac{-i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{i}{4} \right),
\end{align*}
with $s = \arcsin(p)$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.
\end{itemize}

Furthermore, we can construct other examples of 
Pauli dynamical maps
such that the curve of states $|\beta(p)\rangle$ 
can be implemented with a 1PR circuit.
To do it, we only need to choose the three vectors $\vec{a}, \vec{b},\vec{c}$
that satisfy the conditions of  \eref{eq:conditions-vecs}.

For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|\vec{a}|, |\vec{b}|, |\vec{c}|$
such that $|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1$
by selecting two angles $\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and 
defining:
\begin{align*}
|\vec{a}| = \sin \nu \cos \mu, \; |\vec{b}| = \sin \nu \sin \mu , \; |\vec{c}| = \cos \nu.
\end{align*}
\item[2.] We define $\vec{a'} = (|\vec{a}|,0,0,0),$ $\vec{b'} = (0,|\vec{b}|,0,0),$ $\vec{c'} = (0,0,|\vec{c}|,0)$.
\item[3.] Finally, we select a unitary matrix $V$
and use it to define the vectors $\vec{a} = V \vec{a'}, \vec{b} = V \vec{b'}, \vec{c} = V \vec{c'}$.
This way, since the primed vectors are orthogonal and their squared norms add up to one,
so do the unprimed vectors and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}. 
\end{itemize}

Following this procedure for random
angles and unitary matrices $V$, 
we plot four Pauli dynamical maps 
that can be implemented with a 1PR circuit in \fref{fig:curves-random}.
These maps where constructed with the additional condition
of passing through the identity channel.
To do that, we ensure that the vectors also satisfy
$\vec{a} + \vec{b} + \vec{c} = (e^{i \theta},0,0,0)$ with $\theta$ an arbitrary
real number.
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $(e^{i \theta},0,0,0)$, which
corresponds with the identity channel.

To fulfill this additional condition,  we restrict the first row of
$V$ to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
\vec{a} + \vec{b} + \vec{c} = V (\vec{a'} + \vec{b'} + \vec{c'}) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
\end{align*}
The last step is because the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
is obtained by calculating the dot product of the first row of $V$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
one but $V$ preserves the norm.

>>>>

This theorem implies that starting from the state $|0\rangle$,
the only curves of states we could expect to create
with a 1PR circuit are those of the form
\begin{equation}
|\eta(p)\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is},
\label{eq:curve-states}
\end{equation}
with 
\begin{equation}
|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1  \; \text{and} \; \vec{a}, \vec{b}, \vec{c} \; \text{orthogonal vectors},
\label{eq:conditions-vecs}
\end{equation}
and $s = s(p)$ a function of $p$.
Furthermore, we can exhibit a 1PR circuit to create any of these curves of states.
To do it, we can use the circuit of \fref{fig:1PR-circuit} and set the parametrized
rotation $R$ on the last qubit to be controlled by all the other qubits..
Moreover, we define the matrices $A$ and $B$ as:
\begin{align*}
B = (\vec{d}, *,*, \cdots,*), \; 
A = (* , \cdots, *, \vec{c}/|\vec{c}|, \vec{b}/|\vec{b}|, \vec{a}/|\vec{a}|),
\end{align*}
where the column vector $\vec{d}$ is defined as 
$(0,0, \cdots,0 ,|\vec{c}|, |\vec{b}|, |\vec{a}|)^T$
and the asterisks can be filled up in any
way such that these matrices are unitary.
Then, starting from the initial state $|0\rangle = (1,0,0,\cdots,0)$
and applying the circuit (whose matrix is $ARB$), some direct calculations lead us  to 
the resulting curve of states
of \eref{eq:curve-states}.

@@

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
Given this condition, the curve of states of \eref{eq: parametrized state}  needed 
to implement the map
has to be constructed with only one parametrized rotation. 
Therefore, the results of the last section imply that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is},
\end{eqnarray}
where $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors in $\mathbb{C}^{2n}$ 
and $|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2= 1$.

For the particular case of one qubit,
we can show some examples of Pauli dynamical maps
implementable with a 1PR circuit, which are plotted
in \fref{fig:curves}.

@@

\begin{itemize}
\item \textbf{Bit flip map:} 
This dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1
\end{align*}
for $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
$|\beta_0(p)|^2= (1-p)^2$, $|\beta_1(p)|^2 = p$, $|\beta_2(p)|^2 = |\beta_3(p)|^2 = 0$.
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = \left(\sqrt{1-p},\sqrt{p},0,0\right).
\end{align*}
This can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is} \left( \dfrac{1}{2}, - \dfrac{i}{2},0,0 \right) + e^{-is} \left( \dfrac{1}{2}, \dfrac{i}{2},0,0 \right),
\end{align*}
with $s= \arcsin(\sqrt{p})$.
Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
and it can be created with a 1PR circuit.
The exact same thing can be done
for the phase flip and bit phase flip dynamical maps by
changing $\sigma_1$ to
$\sigma_3$ and $\sigma_2$ respectively.

@@

\item \textbf{Parabolic dynamical map:} Finally, we define the parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} (1-p)^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{eqnarray}
|\beta(p)\rangle = \left(\dfrac{1}{2} (1-p) , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2}(1+p) \right).
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle = \left( \dfrac{1}{2},0,0, \dfrac{1}{2} \right) + e^{is} \left( \dfrac{i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{-i}{4} \right) + e^{-is}  \left( \dfrac{-i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{i}{4} \right),
\end{align*}
with $s = \arcsin(p)$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.
\end{itemize}

Furthermore, we can construct other examples of 
Pauli dynamical maps such that it
can be implemented with a 1PR circuit.
To do it, we only need to choose the three vectors $\vec{a}, \vec{b},\vec{c}$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|\vec{a}|, |\vec{b}|, |\vec{c}|$
such that $|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and defining:
\begin{align*}
|\vec{a}| = \sin \nu \cos \mu, \; |\vec{b}| = \sin \nu \sin \mu , \; |\vec{c}| = \cos \nu.
\end{align*}
\item[2.] We define $\vec{a'} = (|\vec{a}|,0,0,0),$ $\vec{b'} = (0,|\vec{b}|,0,0),$ $\vec{c'} = (0,0,|\vec{c}|,0)$.
\item[3.] Finally, we choose a unitary matrix $V$
and use it to define the vectors $\vec{a} = V \vec{a'}, \vec{b} = V \vec{b'}, \vec{c} = V \vec{c'}$.
This way, since the primed vectors are orthogonal and their squared norms add up to one,
so do the unprimed vectors and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}. 
\end{itemize}

Following this procedure for random
angles and unitary matrices $V$, 
we plot four Pauli dynamical maps 
that can be implemented with a 1PR circuit in \fref{fig:curves-random}.
These maps where constructed with the additional condition
of the map passing through the identity channel.
To do that, we ensure that the vectors also satisfy
$\vec{a} + \vec{b} + \vec{c} = (e^{i \theta},0,0,0)$ with $\theta$ an arbitrary
real number.
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $(e^{i \theta},0,0,0)$, which
corresponds with the identity channel.

To fulfill this additional condition,  we restrict the first row of
$V$ to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
\vec{a} + \vec{b} + \vec{c} = V (\vec{a'} + \vec{b'} + \vec{c'}) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
\end{align*}
The last step is because the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
is obtained by calculating the dot product of the first row of $V$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.
